Study of Higgs plus single top production using events with a same sign dimuon at the Large Hadron Collider

### 2019-11-24 tesis_hiram/Abstract/abstract.tex
correccion

% ************************** Thesis Abstract *****************************
% Use `abstract' as an option in the document class to print only the titlepage and the abstract.
%\begin{center}
%	\justifying
We present a study on the production of a Higgs boson plus a single top quark ($tH$) in same sign dimuon channel $\mu^\pm \mu^\pm$ using data published by the CMS experiment at CERN. By studying this
process, we explore a Higgs production mechanism which has not yet been observed
experimentally. The expected sensitivity is estimated by using an Asimov dataset for 35.9 fb$^{-1}$ of proton-proton collisions and is extrapolated to the high luminosity phase of the LHC (HL-LHC).
The sensitivity is also studied for the model with inverted Yukawa coupling $k_t$=-1, where $k_t$ is the top-Higgs coupling parameter modifier, for comparison with the Standard Model.
%\end{center}

>>>>

% ************************** Thesis Abstract *****************************
% Use `abstract' as an option in the document class to print only the titlepage and the abstract.

We present a study on the production of a Higgs boson plus a single top quark ($tH$) in same sign dimuon channel $\mu^\pm \mu^\pm$ using data published by the CMS experiment at CERN. By studying this
process, we explore a Higgs production mechanism which has not yet been observed
experimentally. The expected sensitivity is estimated by using an Asimov dataset for 35.9 fb$^{-1}$ of proton-proton collisions and is extrapolated to the high luminosity phase of the LHC (HL-LHC).
The sensitivity is also studied for the model with inverted Yukawa coupling $k_t$=-1, where $k_t$ is the top-Higgs coupling parameter modifier, for comparison with the Standard Model. For the SM, we obtained an upper limit of 17 on the signal strength with a confidence level of 95$\%$ with respect to the expected value using an integrated luminosity of 35.9 fb$^{-1}$, while with 3000 fb$^{-1}$ we obtained an upper limit of 4.3. In the modified model with $k_t$=-1, we obtained an upper limit of 2.3 using 35.9 fb$^{-1}$, while in the 3000 fb$^{-1}$ case a possible signal could be measured with an uncertainty of 10$\%$.

### 2019-11-24 tesis_hiram/Abstract/resumen.tex
correccion

%\renewcommand{\absnamepos}{empty} % originally center
%\begin{center}
%	\justifying
Se presenta un estudio sobre la producci\'on del boson de Higgs y un top quark ($tH$) en el canal de 2 muones con el mismo signo $\mu^\pm \mu^\pm$ usando datos publicados por el experimento CMS en el CERN.
Estudiando este proceso se explora este mecanismo de producci\'on del boson de Higgs que a\'un no se ha detectado experimentalmente.
La sensibilidad esperada es calculada usando  datos de tipo Asimov para 35.9 fb$^{-1}$ de colisiones de prot\'on-prot\'on y es extrapolada la fase de alta luminosidad del LHC (HL-LHC).
La sensibilidad de la se\~nal es tambi\'en estudiada para el modelo con acoplamiento de Yukawa invertido $k_t$=-1, donde $k_t$ es el modificador del par\'ametro de acoplamiento de top-Higgs, en comparaci\'on con el Modelo Est\'andar.
%\end{center}

>>>>

%\renewcommand{\absnamepos}{empty} % originally center
%\begin{center}
%	\justifying
Se presenta un estudio sobre la producci\'on del boson de Higgs y un top quark ($tH$) en el canal de 2 muones con el mismo signo $\mu^\pm \mu^\pm$ usando datos publicados por el experimento CMS en el CERN.
Estudiando este proceso se explora este mecanismo de producci\'on del boson de Higgs que a\'un no se ha detectado experimentalmente.
La sensibilidad esperada es calculada usando  datos de tipo Asimov para 35.9 fb$^{-1}$ de colisiones de prot\'on-prot\'on y es extrapolada la fase de alta luminosidad del LHC (HL-LHC).
La sensibilidad de la se\~nal es tambi\'en estudiada para el modelo con acoplamiento de Yukawa invertido $k_t$=-1, donde $k_t$ es el modificador del par\'ametro de acoplamiento de top-Higgs, en comparaci\'on con el Modelo Est\'andar. Para el modelo SM, se obtuvo un l\'imite de 17 en la fuerza de la se\~nal a un nivel de confianza de 95$\%$ con respecto al valor esperado usando 35.9 fb$^{-1}$ de luminosidad integrada, mientras que con 3000 fb$^{-1}$ se obtiene un l\'imite de 4.3. Para el modelo modificado con $k_t$=-1, se obtiene un l\'imite de 2.3 usando 35.9 fb$^{-1}$ , mientras que con 3000 fb$^{-1}$  se podr\'ia medir la fuerza de una posible se\~nal con 10$\%$ de incertidumbre.
%\end{center}
